Skill estimation using TrueSkill Through Time: \\ the \proglang{Julia}, \proglang{Python} and \proglang{R} packages (Draft)

### 2021-04-29 doc/article.tex
Title

%% - \title{} in title case
%% - \Plaintitle{} without LaTeX markup (if any)
%% - \Shorttitle{} with LaTeX markup (if any), used as running title
\title{Skill estimation using TrueSkill Through Time: the \proglang{Julia}, \proglang{Python} and \proglang{R} packages}
\Plaintitle{Skill estimation using TrueSkill Through Time: the Julia, Python and R packages}
\Shorttitle{TrueSkill Through Time: the \proglang{Julia}, \proglang{Python} and \proglang{R} packages (Draft)}

@@

  Matias Mazzanti\\
  Departamento de F\'isica\\
  Facultad de Ciencias Exactas y Naturales\\
  Universidad de Buenos Aires\\
  Buenos Aires, Argentina\\

>>>>

%% - \title{} in title case
%% - \Plaintitle{} without LaTeX markup (if any)
%% - \Shorttitle{} with LaTeX markup (if any), used as running title
\title{Skill estimation using TrueSkill Through Time: \\ the \proglang{Julia}, \proglang{Python} and \proglang{R} packages (Draft)}
\Plaintitle{Skill estimation using TrueSkill Through Time:  \\ the Julia, Python and R packages (Draft)}
\Shorttitle{TrueSkill Through Time: the \proglang{Julia}, \proglang{Python} and \proglang{R} packages (Draft)}

@@
